\begin{thebibliography}{9}
\bibitem{bigcmspaper} CMS~Collaboration, {\em The CMS experiment at
    the CERN LHC}, 2008 JINST 3 S08004.
\bibitem{tdr} CMS~Collaboration, {\em CMS: The Tracker Project
    Technical Design Report}, CERN/LHCC 98-06, CMS TDR 5, 15 April
  1998; CMS Collaboration, {\em Addendum to the CMS Tracker TDR}, CERN/LHCC
  2000-016, CMS TDR 5 Addendum 1, 21 February 2000.
%\bibitem{modules} no obvious ref... refer to~\cite{bigcmspaper}.
%\bibitem{sensors} sensor ref out of scope here, refer to~\cite{bigcmspaper}. 
\bibitem{hybrid} U.~Goerlach, {\em Industrial production of front-end
    hybrids for the CMS silicon tracker}, Proceedings of the 9$^{\rm
    th}$ Workshop on Electronics for LHC Experiments, Amsterdam, The
  Netherlands (2003), http://cdsweb.cern.ch/record/720615.
\bibitem{apv} M.J.~French et al., {\em Design and results from the
    APV25, a deep sub-micron CMOS front-end chip for the CMS tracker},
  Nucl. Instr. and Meth. A 466 (2001) 359.
\bibitem{pll} K.~Kloukinas, A.~Marchioro, P.~Moreira and P.~Placidi,
  {\em A 40 MHz clock and trigger recovery circuit for the CMS tracker
    fabricated in a $0.25{\um}$ CMOS technology and using a self
    calibration technique}, in Proceedings of the $5^{\rm th}$
  Workshop on Electronics for LHC Experiments, Snowmass US (1999).
\bibitem{dcu} G.~Magazz\'u, A.~Marchioro and P.~Moreira, {\em The
    detector control unit: an ASIC for the monitoring of the CMS
    silicon tracker}, IEEE Trans. Nucl. Sci. 51 (2004) 1333.
\bibitem{apvmux} see~\cite{bigcmspaper} p. 58. 
\bibitem{pa} {\em Technical Specification For The Cms Tracker Silicon
  Module Pitch Adapters}, IT-3050/EP/CMS (2002);
\bibitem{gantry} A.~Honma et al., {\em An Automated Silicon Module
    Assembly System for the CMS Silicon Tracker}, CMS Note 2002/005.
\bibitem{hip} W.~Adam et al., {\em The effect of highly ionising
    particles on the CMS silicon strip tracker}, Nucl. Instrum. and
  Meth. A 543 (2005) 463.
\bibitem{arc} M.~Axer et al., {\em Testing of FE Hybrids and Si
    detector modules for the CMS Tracker}, Nucl. Instrum. and Meth. A
  485 (2002) 73.
\bibitem{cooli} Cooli - Cold Box Control Serial Interface,
  beissel@physik.rwth-aachen.de, III.Physikalisches Institut B, RWTH
  Aachen (2002).
\bibitem{pllmanual} P.~Placidi, A.~Marchioro and P.~Moreira, {\em CMS
    Tracker PLL Reference Manual},
  http://cmstrackercontrol.web.cern.ch (2000).
\bibitem{db}
  {\em CMS Tracker Database}, http://cmsdoc.cern.ch/$\sim$cmstrkdb.
\end{thebibliography}
