\documentclass[a4paper]{jpconf}
\usepackage{graphicx}


\usepackage{slashed}
\usepackage{subfigure}
%\usepackage{rotating}
\usepackage{multirow}
\usepackage{amsmath}
%\usepackage{units}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{fig/}}

\input{my_macros}
\def\centeron#1#2{{\setbox0=\hbox{#1}\setbox1=\hbox{#2}\ifdim
\wd1>\wd0\kern.5\wd1\kern-.5\wd0\fi
\copy0\kern-.5\wd0\kern-.5\wd1\copy1\ifdim\wd0>\wd1
\kern.5\wd0\kern-.5\wd1\fi}}
\def\ltap{\;\centeron{\raise.35ex\hbox{$<$}}{\lower.65ex\hbox{$\sim$}}\;}
\def\gtap{\;\centeron{\raise.35ex\hbox{$>$}}{\lower.65ex\hbox{$\sim$}}\;}
\def\gsim{\mathrel{\gtap}}
\def\lsim{\mathrel{\ltap}}

\begin{document}
\title{CMS reconstruction improvements for the tracking in large pile-up events}

\author{$^1$D~Giordano and $^2$G~Sguazzoni}

\address{$^1$CERN, Information Technology Department, Experiment Support Group, Geneva, Switzerland}
\address{$^2$INFN, Firenze, Italy}


\ead{domenico.giordano@cern.ch, giacomo.sguazzoni@cern.ch}

\begin{abstract}
The CMS tracking code is organized in several levels, known as
'iterative steps', each optimized to reconstruct a class of particle
trajectories, as the ones of particles originating from the primary
vertex or displaced tracks from particles resulting from secondary
vertices. Each iterative step consists of seeding, pattern recognition
and fitting by a kalman filter, and a final filtering and
cleaning. Each subsequent step works on hits not yet associated to a
reconstructed particle trajectory. The CMS tracking code underwent a
major upgrade needed to make the reconstruction computing load
compatible with the increasing instantaneous luminosity of LHC,
resulting in a large number of primary vertices and tracks per bunch
crossing. The iterative steps have been reorganized and optimized and
an iterative step specialized for the reconstruction of photon
conversion has been added. It is based on the innovative idea to use
an existing track to build up a custom seed in the conversion
hypothesis. For special event reconstruction applications, as the
particle flow algorithm, it is necessary to test the possible
association between a given reconstructed track and an energy deposit
in calorimeters (cluster). The implementation of a k-dimensional tree
in two dimensions allowed the combinatorics of links between tracks
and clusters to be reduced from N*N to N*log(N), where N is the number
of objects. The impact on reconstruction performances are promising
and the prospects for future applications are discussed.
\end{abstract}


\include{introduction}

\include{fall11}

\include{summer12}

\include{glimpse}

\include{conclusions}

\include{bibliography}

\end{document}
